---
title: 'Analysis for Experiment 2'
author: "KN"
date: '`r Sys.Date()`'
output: 
        html_document:
         toc: true
         toc_depth: 3
         toc_float: true
         number_section: true
---

For output from ibex farm 

About
=====
- SPR conducted at Lancers ibex, May 8, 2018  
- 116 participants    
- Target items: 24  
- Filler items: 48  
  


Conditions:  
Ds. Durative × Simplex    
Dr. Durative x Reduplicated  
Cs. Non-durative x Simplex  
Cr. Non-durative x Reduplicated  

[["Ds",1], "DashedSentenceNoSpace",  
{s: "生徒が しばらく 黒板を ちらっと 見たので 先生が カンニングを 疑った。"},  
"Question", {q: "生徒は黒板をしばらく見た。", hasCorrect:0}],
[["Dr",1], "DashedSentenceNoSpace",  
{s: "生徒が しばらく 黒板を ちらちら 見たので 先生が カンニングを 疑った。"}, "Question",  
{q: "生徒は黒板をしばらく見た。", hasCorrect:0}],
[["Cs",1], "DashedSentenceNoSpace",  
{s: "生徒が その時 黒板を ちらっと 見たので 先生が カンニングを 疑った。"},  
"Question", {q: "生徒は黒板をしばらく見た。", hasCorrect:1}],
[["Cr",1], "DashedSentenceNoSpace",  
{s: "生徒が その時 黒板を ちらちら 見たので 先生が カンニングを 疑った。"},  
"Question", {q: "生徒は黒板をしばらく見た。", hasCorrect:1}],  





##### Load libraries

```{r}
#library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(ggplot2)
library(reshape)
library(gdata)      
library(MASS)
```


##### Declare the expt name that is relevant.
```{r}
ex<-"e"

# critical region
criticalregion<-4

# how far from the critical region do you want the plot to cover?
crplus<-3

# plot legend（凡例）のならび順はデフォルトではアルファベット順
# 逆順にしたい場合はここを1にする
revorderA <- 1  # ab vs cd
revorderB <- 1  # ac vs bd


```


##### Trimming criteria
```{r}
# Trim bad subjects: data<-subset(data,SubjCA>=trimSubjCA)
# No trimming: trimSubjCA <- 0
trimSubjCA <- 200/3
# Trim bad subjects: data<-subset(data,SubjExptCA>=trimSubjExptCA)
# No trimming: trimSubjExptCA <- 0
trimSubjExptCA <- 0

# Trim slow subjects: data<-subset(data,SubjRTZS<trimSubjRTZS)
# (Virtually) No trimming: trimSubjRTZS <- 99
trimSubjRTZS <- 3

# Trim slow subjects: data<-subset(data,SubjRTmean<trimSubjRTmean)
# (Virtually) No trimming: trimSubjRTZS <- 10000
trimSubjRTmean <- 10000


# Trim incorrectly answered trials?  if( trimincorrect == 1 ){ rt_data<-subset(rt_data,correct==100) }
# No trimming: trimincorrect <- 0
trimincorrect <- 1

# Trim extreme RTs rt_data<-subset(rt_data_notrim,rt>=RTlowerbound & rt<=RTupperbound)
# (Virtually) No trimming: upperboundRT <- 100000
upperboundRT <- 10000
# No trimming: upperboundRT <- 100000
# No trimming: lowerboundRT <- 0
lowerboundRT <- 150

# Then RxC z-scores will be computed
# Trim based on zs in each condition x region cell d<-subset(rt_data,RxCzs<trimRxCzs)
# (Virtually) No trimming: trimRxCzs <- 99
trimRxCzs <- 3

# RT transformation
tf <- "none"  # No transformation
#tf <- "log"   # Log transformation
#tf <- "log10"  # Log10 transformation
#tf <- "negreciprocal" # Negative reciprocal *1000

# Want to center the spillover? (Usually yes)
spillovercentering <- 1

# Want to z-transform the spillover?
spilloverztransform <- 1

```


##### Exclude specific users
```{r}
#exsubj <- c(12,22,32,42,47,50,51)
```


##### Load data:

```{r}
alldata<-read.csv("alldata.csv",header=T)
alldata<-alldata[,-1]
alldata$item<-as.numeric(alldata$item)
itemdata<-read.csv("itemdata.csv")
itemdata<-itemdata[,-1]
# 標準化（z値化）
# 注：scale()[,1]としているのは，scale()は行列を返すので，「列1だけ出力おねがい」という意味
itemdata$Itemvalue<-scale(itemdata$Itemvalue, center = T, scale = T)[,1]
alldata <- merge(alldata,itemdata,all=T);

```

##### Exclude specific users
```{r}
#alldata <- subset(alldata, !(subj%in%exsubj))
```




Isolate the data from the relevant experiment
=============================================
```{r}
data<-subset(alldata,expt==ex)
unique(data$expt)
```

Isolate conditions 
=============================================
```{r}
#data<-subset(data,cond%in%c("a","b","d","e","f","h"))
#unique(data$cond)
```



Subj exclusion
==============


##### before trimming
Subject number before trimming
```{r}
unique(data$subj)
length(unique(data$subj))
```


##### trim by CA

```{r}
data<-subset(data,SubjCA>=trimSubjCA)
unique(data$subj)
length(unique(data$subj))
data<-subset(data,SubjExptCA>=trimSubjExptCA)
unique(data$subj)
length(unique(data$subj))
```

#### comprehension accuracy for each condition after the subject trimming

```{r}
check<-subset(data,region==1)
ddply(check, .(cond), summarize, mean=mean(correct))

check$correct<-check$correct/100


check$adv<-ifelse(check$cond%in%c("Dr","Ds"),1,-1) #Dur vs. nondur
check$ideo<-ifelse(check$cond%in%c("Ds","Cs"),1,-1) #Simplex vs. Redup


checkglm<-glm(formula = correct ~ adv*ideo, data = check, family = binomial)
summary(checkglm)
```


#### mean accuracy rate for each condition
```{r}
cddata<-subset(data,cond =="Cs",select=c(subj, correct, region))
cddata<-subset(cddata, region=="1")
cddata
```

```{r}
numsubj<-length(cddata$subj)
sumcorrect<-sum(cddata$correct)
sumcorrect/numsubj
```

```{r}
cddata<-subset(data,cond =="Cr",select=c(subj, correct, region))
cddata<-subset(cddata, region=="1")
cddata
```

```{r}
numsubj<-length(cddata$subj)
sumcorrect<-sum(cddata$correct)
sumcorrect/numsubj
```

```{r}
cddata<-subset(data,cond =="Ds",select=c(subj, correct, region))
cddata<-subset(cddata, region=="1")
cddata
```

```{r}
numsubj<-length(cddata$subj)
sumcorrect<-sum(cddata$correct)
sumcorrect/numsubj
```

```{r}
cddata<-subset(data,cond =="Dr",select=c(subj, correct, region))
cddata<-subset(cddata, region=="1")
cddata
```

```{r}
numsubj<-length(cddata$subj)
sumcorrect<-sum(cddata$correct)
sumcorrect/numsubj
```

##### trim by RTZS

```{r}
data<-subset(data,SubjRTZS<=trimSubjRTZS)
unique(data$subj)
length(unique(data$subj))
```


##### trim by RTmean

```{r}
data<-subset(data,SubjRTmean<=trimSubjRTmean)
unique(data$subj)
length(unique(data$subj))
```



Reading time summary
====================

```{r}
rt_data<-data
```

##### Make sure factors are treated as factors
```{r}
rt_data$subj<-factor(rt_data$subj)
rt_data$expt<-factor(rt_data$expt)
rt_data$item<-factor(rt_data$item)
rt_data$cond<-factor(rt_data$cond)
rt_data$word<-factor(rt_data$word)
```

##### Correctly answered trials only? (trimincorrect)

Note: if you do this trimming at this point, it precedes the z-score computation.



```{r}
before <- length(data$rt)
before
```


```{r}
rt_data<-subset(data,correct==100)

```

```{r}
after <- length(rt_data$rt)
after
```

```{r}
(before-after)*100/before
```

##### RT trimming?  
100msを切るRTが見受けられるのでさすがにカットしたほうが良いかと。
```{r}
subset(rt_data,rt<200 & region==1,c("expt","cond","region","rt"))
subset(rt_data,rt<200 & region==2,c("expt","cond","region","rt"))
subset(rt_data,rt<200 & region==3,c("expt","cond","region","rt"))
subset(rt_data,rt<200 & region==4,c("expt","cond","region","rt"))
subset(rt_data,rt<200 & region==5,c("expt","cond","region","rt"))
subset(rt_data,rt<200 & region==6,c("expt","cond","region","rt"))

subset(rt_data,rt>3000 & region==1,c("expt","cond","region","rt"))
subset(rt_data,rt>3000 & region==2,c("expt","cond","region","rt"))
subset(rt_data,rt>3000 & region==3,c("expt","cond","region","rt"))
subset(rt_data,rt>3000 & region==4,c("expt","cond","region","rt"))
subset(rt_data,rt>3000 & region==5,c("expt","cond","region","rt"))
subset(rt_data,rt>3000 & region==6,c("expt","cond","region","rt"))

tapply(rt_data$rt, rt_data$region, mean)
tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean)
```

rt trimming

```{r}
rt_data_notrim <- rt_data

rt_data<-subset(rt_data_notrim,rt>=lowerboundRT & rt<=upperboundRT)

```

Generate z-scores for variable A using the scale() function
scale(A, center = TRUE, scale = TRUE)

Be aware that this z-score computation per region x cond cell is { before / after } the yes/no trimming.

```{r}
myRT <- c()
newdataframe <- c()
for(i in unique(rt_data$region)){   
  for(j in unique(rt_data$cond)){
    # abstract rt column in the region x cond cell
    myRT <- subset(rt_data, region==i & cond==j);
    # compute z-score; [,1]を付けるのはscale()が行列データを返すので列1だけ出力してという意味
    myRT$RxCzs <- scale(myRT$rt, center = T, scale = T)[,1];
    # 蓄積
    newdataframe<-rbind(newdataframe,myRT);
    }
}; 

rt_data <- merge(rt_data,newdataframe,all=T)
length(unique(rt_data$subj))
```

##### check outliers
```{r}
bs <- rt_data[which(rt_data$RxCzs >3),]
bs <- bs[c("subj","item","region","cond","rt","RxCzs")]
bs[order(bs$region,bs$cond,bs$RxCzs),]
```

```{r}
bs <- rt_data[which(rt_data$RxCzs >5),]
bs <- bs[c("subj","item","region","cond","rt","RxCzs")]
bs[order(bs$region,bs$cond,bs$RxCzs),]
```


##### rt trimming based on RxCzs
```{r}
tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean)

rt_data<-subset(rt_data,RxCzs<trimRxCzs)

tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean)
mean(subset(rt_data,region==5&cond=="h")$rt)

```

```{r}
(length(rt_data_notrim$rt)-length(rt_data$rt))*100/length(rt_data_notrim$rt)
```


##### log transform
```{r}
ifelse(tf=="log",rt_data$rt<-log(rt_data$rt),
       ifelse(tf=="log10",rt_data$rt<-log10(rt_data$rt),
              ifelse(tf=="negreciprocal",rt_data$rt<- -1000/rt_data$rt,tf<-"none")))

if(tf!="none"){ tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean) }

ifelse(tf=="log",RTlabel<-"Log-transformed RTs",
       ifelse(tf=="log10",RTlabel<-"Log_10-transformed RTs",
              ifelse(tf=="negreciprocal",RTlabel<-"Neg-reciprocal RTs",RTlabel<-"RTs(ms)")))



if(tf!="none"){ tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean) }
```


##### choose spillover in accordance of the choice log transformation 
```{r}
# First, change the value of spilloverraw under lowerboundRT to the value of lowerboundRT because we do not overestimate the negative spillover effects
rt_data$spilloverraw[rt_data$spilloverraw<lowerboundRT]<-lowerboundRT

ifelse(tf=="log",rt_data$spillover<-log(rt_data$spilloverraw),
       ifelse(tf=="log10",rt_data$spillover<-log10(rt_data$spilloverraw),
              ifelse(tf=="negreciprocal",rt_data$spillover<- -1000/rt_data$spillover,rt_data$spillover<-rt_data$spilloverraw)))

head(rt_data) %>%
  dplyr::select(subj,expt,item,cond,region,rt,spilloverraw,spillover) 


# centering
ifelse(spilloverztransform == 1,
       rt_data$spillover<-scale(rt_data$spillover, center=T, scale=T),
       ifelse(spillovercentering == 1, 
              rt_data$spillover <- scale(rt_data$spillover, center=T, scale=F),
              rt_data$spillover <- rt_data$spillover))

head(rt_data) %>%
  dplyr::select(subj,expt,item,cond,region,rt,spilloverraw,spillover) 



#if(tf!="none"){ tapply(rt_data$rt, paste(rt_data$region, rt_data$cond), mean) }
```


## Summary (interim)

のちにtrimmingをする（かもしれない）ので，このファイルの最後でもういちどサマリーとプロットの最終盤を生成します。

##### Extract data for summary

###### Critical region plus 3
```{r}
rtg <- subset(rt_data,region<=criticalregion+crplus)

```

##### better comprehender?
```{r}
# rtg$ExptCAmedian
# rtg$ExptCAmean
# rtg <- subset(rtg,SubjExptCA>=ExptCAmedian)
```


##### summary

```{r}
# Raw rt version
rt_data_summary <- ddply(rtg, .(cond,region), summarise, N=length(rt), mean=mean(rt), sd=sd(rt), se=sd/sqrt(N),ci=qt(0.975,df=N-1)*se)
```

##### Coding conditions for plot labels
```{r}
rt_data_summary$A<-ifelse(rt_data_summary$cond%in%c("Cr","Cs"),"Non-durative","Durative")
rt_data_summary$B<-ifelse(rt_data_summary$cond%in%c("Cr","Dr"),"Reduplicated","Simplex")
rt_data_summary$Conditions<-paste(rt_data_summary$A,rt_data_summary$B,sep=":")
rt_data_summary$B

# Change the order of the legend labels
if( revorderA == 1 ){  
  rt_data_summary$A<-factor(rt_data_summary$A, levels=rev(levels(factor(rt_data_summary$A))))}
if( revorderB == 1 ){  
  rt_data_summary$B<-factor(rt_data_summary$B, levels=rev(levels(factor(rt_data_summary$B))))
}


# Factor labels in the plots
Alabel<-"Temp Adverb"  
Blabel<-"Ideophone"  

rt_data_summary
#rrt_data_summary
```


## Plots

See the following references for ggplot codes:

http://www.cookbook-r.com/Graphs/Shapes_and_line_types/

http://meme.biology.tohoku.ac.jp/students/iwasaki/rstats/ggplot2.html


##### Mean RTs
Base
```{r}
g <- ggplot(rt_data_summary,aes(x=region,y=mean,group=Conditions))
```

Add lines
```{r}
g <- g + geom_line(size=1,aes(linetype=A),position = position_dodge(.3))
g <- g + scale_linetype_manual(values=c("dotdash","solid"))
g <- g + labs(linetype=Alabel)
```

Add points
```{r}
g <- g + geom_point(size=5,aes(shape=B,fill=B),position = position_dodge(.3))
g <- g + scale_shape_manual(values=c(21,24,24,25))
g <- g + scale_fill_manual(values=c("white","black","white","black"))
g <- g + labs(shape=Blabel)
g <- g + labs(fill=Blabel)
```



Add error bars
```{r}
g <- g + geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.3,position = position_dodge(.3))
```

Adjust x-axis breaks and labels
```{r}
g <- g + scale_x_continuous(breaks=seq(1, 8, by=1),labels=c("Subj", "Temp Adv",
                              "Mod", "Ideo", "Verb", "6","7","8"))

```

Create Theme

```{r}
g <- g + theme(      
                 # 背景を消す
                 panel.background = element_rect(fill = "white"),
                 panel.border = element_blank(), axis.line = element_line(),
                 # 凡例の設定
                 legend.position    = c(1, 1),
                 legend.justification = c(1,1),
                 #legend.title = element_blank(), 
                 legend.title = element_text(family = "Times", size = 15),
                 legend.text = element_text(size = 15, family="Times"),
                 legend.key = element_blank(), 
                 # テキスト形式の設定
                 axis.title.x = element_text(family = "Times", size = 20), 
                 axis.title.y = element_text(family = "Times",size = 20), 
                 axis.text.x = element_text(angle =   45, size = 15, hjust = 1,family = "Times"), 
                 axis.text.y = element_text(size = 15, hjust = 0.5, family = "Times"),
              )

```


Adjust appearance
```{r}
#g <- g + theme_classic(base_size=20, base_family="HiraKakuProN-W3")
#g <- g + theme(base_size=20, base_family="Times", axis.text.x = element_text(angle = 45, hjust = 1))
g <- g + labs(x="Region", y="RT (ms)")
print(g)
ggsave("Figure6_RawRT.png")
```


##### Interaction
Base
```{r}
rtg <- subset(rt_data_summary,region==criticalregion)
g <- ggplot(rtg,aes(x=A,y=mean,group=Conditions))
```

Add lines
```{r}
g <- g + geom_line(size=1,aes(group=B,linetype=B))
g <- g + scale_linetype_manual(values=c("dotdash","solid"))
g <- g + labs(linetype=Blabel)
```

Add points
```{r}
g <- g + geom_point(size=8,aes(shape=B,fill=B),position = position_dodge(.2))
g <- g + scale_shape_manual(values=c(21,24,24,25))
g <- g + scale_fill_manual(values=c("white","black","white","black"))
g <- g + labs(shape=Blabel)
g <- g + labs(fill=Blabel)
```

Add error bars
```{r}
g <- g + geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.1,position = position_dodge(.2))
```

Adjust x-axis breaks
```{r}
#g <- g + scale_x_continuous(breaks=seq(1, 10, by=1))
```

Adjust appearance
```{r}
g <- g + theme_classic(base_size=20, base_family="HiraKakuProN-W3")
g <- g + theme_classic(base_size=20, base_family="Times")
g <- g + theme(aspect.ratio = 1) #Ratio of y-bar to x-bar=1
g <- g + labs(x="Temporal adverb", y=RTlabel)
print(g)
ggsave("Figure7_R4.png")
```




##### Interaction
Base
```{r}
rtg <- subset(rt_data_summary,region==criticalregion+1)
g <- ggplot(rtg,aes(x=A,y=mean,group=Conditions))
```

Add lines
```{r}
g <- g + geom_line(size=1,aes(group=B,linetype=B))
g <- g + scale_linetype_manual(values=c("dotdash","solid"))
g <- g + labs(linetype=Blabel)
```

Add points
```{r}
g <- g + geom_point(size=8,aes(shape=B,fill=B),position = position_dodge(.2))
g <- g + scale_shape_manual(values=c(21,24,24,25))
g <- g + scale_fill_manual(values=c("white","black","white","black"))
g <- g + labs(shape=Blabel)
g <- g + labs(fill=Blabel)
```

Add error bars
```{r}
g <- g + geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.1,position = position_dodge(.2))
```

Adjust x-axis breaks
```{r}
#g <- g + scale_x_continuous(breaks=seq(1, 10, by=1))
```

Adjust appearance
```{r}
g <- g + theme_classic(base_size=20, base_family="HiraKakuProN-W3")
g <- g + theme_classic(base_size=20, base_family="Times")
g <- g + theme(aspect.ratio = 1) #Ratio of y-bar to x-bar=1
g <- g + labs(x="Temporal abverb", y=RTlabel)
print(g)
ggsave("Figure8_R5.png")
```


##### Interaction
Base
```{r}
rtg <- subset(rt_data_summary,region==criticalregion+2)
g <- ggplot(rtg,aes(x=A,y=mean,group=Conditions))
```

Add lines
```{r}
g <- g + geom_line(size=1,aes(group=B,linetype=B))
g <- g + scale_linetype_manual(values=c("dotdash","solid"))
g <- g + labs(linetype=Blabel)
```

Add points
```{r}
g <- g + geom_point(size=8,aes(shape=B,fill=B), position = position_dodge(.2))
g <- g + scale_shape_manual(values=c(21,24,24,25))
g <- g + scale_fill_manual(values=c("white","black","black","white"))
g <- g + labs(shape=Blabel)
g <- g + labs(fill=Blabel)
```

Add error bars
```{r}
g <- g + geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.1, position = position_dodge(.2))
```

Adjust x-axis breaks
```{r}
#g <- g + scale_x_continuous(breaks=seq(1, 10, by=1))
```

Adjust appearance
```{r}
g <- g + theme_classic(base_size=20, base_family="HiraKakuProN-W3")
g <- g + theme_classic(base_size=20, base_family="Times")
g <- g + theme(aspect.ratio = 1) #Ratio of y-bar to x-bar=1
g <- g + labs(x="Temporal adverb", y=RTlabel)
print(g)
ggsave("Figure9_R6.png")
```

##### Plot the mean RTs against Itemvalue
```{r}
itemvaluedata <- subset(rt_data,region<=criticalregion+crplus)

itemvalue_data_summary <- ddply(itemvaluedata, .(Itemvalue,cond,region), summarise, N=length(rt), mean=mean(rt), sd=sd(rt), se=sd/sqrt(N),ci=qt(0.975,df=N-1)*se)
```

```{r}
cregion <- subset(itemvalue_data_summary,region==criticalregion+1)
g <- ggplot(cregion,aes(x=Itemvalue,y=mean,shape=cond,fill=cond,linetype=cond))
g <- g + geom_point()

# Manually specify the shapes, colors, linetypes
#g <- g + scale_shape_manual(values=c(25,22))
#g <- g + scale_fill_manual(values=c("grey","black"))
#g <- g + scale_linetype_manual(values=c("dashed","solid"))

# smoother
g <- g + geom_smooth(method="lm",colour="black",size=0.5)

# theme
g <- g + theme_classic(base_size=20, base_family="Times")

# labels
g <- g + xlab("Itemvalue")
g <- g + ylab("RTs")
g <- g + labs(type="Dependency type")

print(g)
```





##### Plot the mean RTs against Itemvalue: Nondurative only
```{r}
itemvaluedata <- subset(rt_data,region<=criticalregion+crplus)

itemvalue_data_summary <- ddply(itemvaluedata, .(Itemvalue,cond,region), summarise, N=length(rt), mean=mean(rt), sd=sd(rt), se=sd/sqrt(N),ci=qt(0.975,df=N-1)*se)
```

```{r}
cregion <- subset(itemvalue_data_summary,region==criticalregion+1)
cregion <- subset(cregion, cond=="Cr"|cond=="Cs")
g <- ggplot(cregion,aes(x=Itemvalue,y=mean,shape=cond,fill=cond,linetype=cond))
g <- g + geom_point()

# Manually specify the shapes, colors, linetypes
#g <- g + scale_shape_manual(values=c(25,22))
#g <- g + scale_fill_manual(values=c("grey","black"))
#g <- g + scale_linetype_manual(values=c("dashed","solid"))

# smoother
g <- g + geom_smooth(method="lm",colour="black",size=0.5)

# theme
g <- g + theme_classic(base_size=20, base_family="Times")

# labels
g <- g + xlab("Itemvalue")
g <- g + ylab("RTs")
g <- g + labs(type="Dependency type")

print(g)
```



### Analysis 



Coding factors 
-------------------------------

##### CONDITIONS:

```{r}
rt_data$Adv<-ifelse(rt_data$cond%in%c("Dr","Ds"),1,-1)
rt_data$Ideo<-ifelse(rt_data$cond%in%c("Ds","Cs"),1,-1)

# For pairwise comparisons
rt_data$simplexVSredup_dur <-ifelse(rt_data$Adv==1,
                          ifelse(rt_data$Ideo==1,1,-1),
                          0)
rt_data$simplexVSredup_nondur <-ifelse(rt_data$Adv==-1,
                          ifelse(rt_data$Ideo==1,1,-1),
                          0)
rt_data$durVSnondur_simplex <-ifelse(rt_data$Ideo==1,
                          ifelse(rt_data$Adv==1,1,-1),
                          0)
rt_data$durVSnondur_redup <-ifelse(rt_data$Ideo==-1,
                          ifelse(rt_data$Adv==1,1,-1),
                          0)



```

rt_data check
```{r}
dc <- subset(rt_data,cond=="Cr",c(cond,word,Adv,Ideo))
head(dc, n=7)
dc <- subset(rt_data,cond=="Cs",c(cond,word,Adv,Ideo))
head(dc, n=7)
dc <- subset(rt_data,cond=="Dr",c(cond,word,Adv,Ideo))
head(dc, n=7)
dc <- subset(rt_data,cond=="Ds",c(cond,word,Adv,Ideo))
head(dc, n=7)

```




##### Make sure factors are treated as factors
```{r}
rt_data$subj<-factor(rt_data$subj)
rt_data$expt<-factor(rt_data$expt)
rt_data$item<-factor(rt_data$item)
rt_data$cond<-factor(rt_data$cond)
rt_data$word<-factor(rt_data$word)
```

#### Critical(Ideophone) region 
```{r}
cregion<-subset(rt_data,region==criticalregion)
```

##### Check words
```{r}
sort(unique(cregion$word))
```


##### Max model


```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)

(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```




#### Verb region
```{r}
cregion<-subset(rt_data,region==criticalregion+1)
```

##### Check words
```{r}
sort(unique(cregion$word))
```



##### Max model


```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)

(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)

```

```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+Adv:Itemvalue+Ideo:Itemvalue+Adv:Ideo:Itemvalue+Itemvalue+
           (1+Adv+Ideo+Adv:Ideo+Adv:Itemvalue+Ideo:Itemvalue+Adv:Ideo:Itemvalue+Itemvalue|subj),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)
(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)

```


```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+Adv:Itemvalue+Ideo:Itemvalue+Adv:Ideo:Itemvalue+Itemvalue+
           (1+Adv+Ideo+Adv:Ideo|subj),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)
(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)

```

```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+Adv:Itemvalue+Ideo:Itemvalue+Adv:Ideo:Itemvalue+Itemvalue+
           (1+Adv+Ideo+Adv:Ideo|subj),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)
(step_res <- step(mm, reduce.fixed = T))
final <- get_model(step_res)
summary(final)
anova(final)

```

#### Ideo x itemvalue in non-durative

```{r}

mm<-lmer(rt~simplexVSredup_dur:Itemvalue+simplexVSredup_nondur:Itemvalue+Adv+Ideo+Itemvalue+Adv:Itemvalue+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)
(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)

```


```{r}

ndcregion <- subset(cregion, Adv==-1)

mm<-lmer(rt~Ideo+Ideo:Itemvalue+Itemvalue+
           (1+Ideo+Ideo:Itemvalue+Itemvalue|subj),
           control=lmerControl(optimizer="bobyqa"),
           ndcregion)
summary(mm)
(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)

```

##### Post hoc multiple pairwise comparisons to test the interaction
```{r}
mmm<-lmer(rt~simplexVSredup_dur+simplexVSredup_nondur+Adv+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mmm)

(step_res <- step(mmm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```

```{r}
mmm<-lmer(rt~durVSnondur_simplex+durVSnondur_redup+Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mmm)

(step_res <- step(mmm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```
####Singleverb 
```{r}
singlev<-subset(cregion,Itemvalue<0)
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           singlev)
summary(mm)

(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```

####Plural verb 
```{r}
pluralv<-subset(cregion,Itemvalue>=0)
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           pluralv)
summary(mm)

(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```




#### Spillover region
```{r}
cregion<-subset(rt_data,region==criticalregion+2)
```

##### Check words
```{r}
sort(unique(cregion$word))
```


##### Max model


```{r}
mm<-lmer(rt~Adv+Ideo+Adv:Ideo+
           (1+Adv+Ideo+Adv:Ideo|subj)+(1+Adv+Ideo+Adv:Ideo|item),
           control=lmerControl(optimizer="bobyqa"),
           cregion)
summary(mm)

(step_res <- step(mm, reduce.fixed = F))
final <- get_model(step_res)
summary(final)
anova(final)


```





